Applying Deep Learning to Acoustic Analysis in the PICO-60 Dark Matter Detector

### 2018-08-07 documentation/paper.tex
Added horizontal lines to table

\begin{tabular}{|l|l|l|l|}
    Technique & Max Accuracy & Max Mean by Run & $dim(\varsigma)=128$ Errors versus 256 \\
    Gravitational Differentiation & 98\% & 96\% & 64\% Increase \\
    Iterative Cluster Nucleation & 100\% & 98\% & 85\% Increase \\
    Original PICO-60 NN & X\% & N/A & N/A
\end{tabular}

>>>>

\begin{tabular}{|l|l|l|l|}
    \hline
    Technique & Max Accuracy & Max Mean by Run & $dim(\varsigma)=128$ Errors versus 256 \\
    \hline
    Gravitational Differentiation & 98\% & 96\% & 64\% Increase \\
    \hline
    Iterative Cluster Nucleation & 100\% & 98\% & 85\% Increase \\
    \hline
    Original PICO-60 NN & TODO\% & N/A & N/A \\
    \hline
\end{tabular}
